---
title: "Lab Report Knapsack"
author: "Lech Kaczmarczyk and Elis Carlberg Larsson"
abstract: >
  This package solves knapsack problem in three different ways.
  
  Package version: `r packageVersion("lab6.knapsack")`
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab Report Knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab6.knapsack)
```
---
## Brute Force Knapsack
**Question:** How much time does it takes to run the algorithm for n = 16 objects?
**Answer:** Initially (prior to implementin paralelization), it took 0.105761s.
We later compared the performance of the final algorithm with paralelization (`parallel = TRUE`) and without paralelization (`parallel = FALSE`). Results below:

```
# test.function.normal <- function(){
#         start <-Sys.time()
#         brute_force_knapsack(x = test_knapsack[1:24,], W = 3500, parallel = FALSE)
#         end <-Sys.time()
#         return(end-start)
# }
#
# test.function.parallel <- function(){
#         start <-Sys.time()
#         brute_force_knapsack(x = test_knapsack[1:24,], W = 3500, parallel = TRUE)
#         end <-Sys.time()
#         return(end-start)
# }

# > print(paste("24 objects without parallelization takes", mean(replicate(3, test.function.normal()))))
# [1] "24 objects without parallelization takes 2.08253846168518" (minutes)
# > print(paste("24 objects with parallelization takes", mean(replicate(3, test.function.parallel()))))
# [1] "24 objects with parallelization takes 31.5325496196747" (seconds)
```
**Answer:** Parelelization led to approx. 4x improvement in the function performace for n = 24 objects.


## Greedy Knapsack
**Question:** How much time does it takes to run the greedy algorithm for n = 1000000 objects?

```
# RNGversion(min(as.character(getRversion()),"3.5.3"))
# set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
# ##old sampler used for backward compatibility
# ## suppressWarnings() can be used so that the above warning is not displayed set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
# n <- 1000000
# knapsack_1000000 <-
#         data.frame(
#                 w=sample(1:4000, size = n, replace = TRUE),
#                 v=runif(n = n, 0, 100000)
#         )
#
# test.function <- function(){
#         start <-Sys.time()
#         greedy_knapsack(x = knapsack_1000000, W = 3500)
#         end <-Sys.time()
#         return(end-start)
# }
#
# mean(replicate(10, test.function()))
# [1] 0.1728671
```
**Answer:** It takes approx. 0.17s to run the greedy algorithm for n = 1000000 objects.
